Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-12-11 paper/manuscript.tex
Updates from Overleaf

Furthermore, are
available computational resources sufficient that throughput will be

@@

Running binding FE calculations in a drug discovery application will typically require the use of software or tools to facilitate the calculations of many compounds. The commercial implementation from Schrodinger, FEP+, uses a graphical user interface and once the user has calculated any missing force field parameters, calculations can be prepared and submitted within minutes. The software builds the network of perturbations, connecting similar compounds based on LOMAP methodology~\cite{liu2013lead}, all inputs for the Desmond simulations are built automatically and the job can be saved or run immediately on available GPUs. The cost of this software is often prohibitive but alternative tools are becoming available to allow relatively straight forward running of alchemical FE calculations with other software~\cite{gapsys2015pmx, loeffler2015fesetup} (CITE New Merz paper, cite PMX paper Vytas and Bert de Groot, cite FESETUP, cite FEanalysis). One consideration at this point is to define the perturbations suitable for the application. For instance, if the goal is to accurately assess the relative binding energy of a small number of compounds, possibly with challenging synthesis, the map of perturbations may contain as many connections between compounds as affordable. However, when running calculations on hundreds of compounds a so called ‘star-map’ can be used that just contains one connection per compound: perturbing every compound to a central ligand, typically the crystal structure ligand. In this way the top-ranking examples can be readily identified and submitted to additional calculations in a second round. 

@@

As discussed above for drug discovery applications, binding free energy calculations using a congeneric set of ligands are likely to be most suited to a relative free energy protocol (see~\ref{sec:step2}). Other than the choice of forcefield for the parameterization of the ligands, some care has to be taken selecting binding poses for these ligands. Generally a common assumption for a congeneric series is that the binding mode is conserved. Therefore, if an X-ray structure of one of the ligands is available, this should be used to position the ligands in the putative binding site in an energetically reasonable conformation that entails no steric or electrostatic mismatch with the receptor. Checking the X-ray structure versus the experimental electron densities is important, as the resolution of part of the ligand or important sidechains may be based on the interpretation of the crystallographer rather than the available electron density. For example, looking at a cyclohexane ring density, a chair conformation is vastly more likely than that of a boat and may just be poorly assigned.

Generally, binding modes within congeneric series are conserved~\cite{}, however, exceptions exist~\cite{}, and weaker binding compounds are more likely to adopt different binding modes (REFS). There may also be ambiguity about the relative orientation of substituents. A known issue involves a 180 degree flip in the dihedral angle of a 6-membered aromatic ring leading to a different spatial position of ortho- or meta- substituents that otherwise should overlap within a series. The 180 degree flip of the ring may not occur enough during simulations to overcome the starting configuration bias. Another scenario may be equatorial and axial substituted saturated rings (e.g. cyclohexane derivatives). This situation may be addressed by explicitly modelling different binding modes of the same ligand and combining later computed free energy differences for different binding modes into a relative free energies of binding (CITE Kaus et al J. Chem. Theory Comput. 2015, 11, 6, 2670-2679).

Congeneric series can contain stereoisomers or enantiomers, making sure that you model the correct one is important. For racemates, the relative abundance of each stereoisomer is normally not known. Therefore, the experimental activity associated with just one conformation is more uncertain. However, the modeling typically uses just the bioactive conformation that best fits the active site. Clearly this introduces the chance for higher error versus experiment. Nevertheless, if all compounds in the congeneric series are racemic, originating from similar synthetic procedures with an expected similar abundance of stereoisomers, then the differences may cancel and the trend in calculated and observed binding energies may be robust. Nevertheless, we can see that care and further testing is needed in this scenario, and the quality of the predictions may suffer.   
\todo[inline, color=green!20]{Question: What is best practice here? I tend to pick one enantiomer and just model that, but experimentally they may have used a racemic mixture?}

@@

Input coordinates for a congeneric series may be generated by docking calculations, or by ligand alignment using maximum common substructure algorithms. As mentioned in the drug discovery section, the latter tends to produce alignments that are more conserved and more consistent free energy changes across a dataset, but will struggle to yield reasonable results for relative binding free energy calculations that involve a significant binding mode rearrangement. This may also lead to steric clashes with the receptor coordinates of the reference ligand if structural rearrangements are needed to accommodate different members of the congeneric series. Small steric clashes may be resolved during subsequent simulation equilibration prior to data collection but there is a risk that the complex relaxes to an alternative metastable state.

An additional consideration arises for single topology relative free energy calculations. In this class of alchemical free energy calculations it is necessary to generate a molecular topology that may describe the initial and final states of the perturbation (see 7.1.1). In cases where the end-states have high topological similarity and high structural overlap this is relatively straightforward and typically handled by use of maximum common substructure calculations. In situations where the end-state topologies differ significantly, or there is relatively little spatial overlap between the two end-states some user intervention may be necessary to produce a satisfactory input topology.

If the binding site location is uncertain but the structure of the receptor is well defined and plausible binding sites are identified, it may be more useful to chose an absolute free energy protocol to compute the standard free energy of binding of the ligand to a set of binding sites. This requires the user to prepare input files describing the bound conformation in different putative binding sites (REF). The apparent binding free energy of the ligand may be obtained by combining the individual binding site free energies, which also indicate where the ligand is more likely to bind. In this case a docking program can generate initial structures. Different commercial and none commercial tools are available, such as: rDock, Autodock Vina, Glide, or Flare to name a few~\cite{ruiz-carmona2014rdock, trott2010autodock, friesner2004glide, cheeseright2006molecular}. 
If the putative binding sites are not apparent, for instance due to significant induced-fit effects, it may be challenging to obtain meaningful free energies of binding. One may have to account for the free energy change for forming a binding site in the target receptor which may not be feasible in FE simulation timescales. Another key application for absolute binding free energies is to study chemically different ligands, that do not share a common scaffold, but bind at the same site or the same site of similar proteins (CITE Aldeghi...Biggin BRD study).

\subsection*{Free energies of hydration or partition coefficients}
Preliminary considerations necessary for using free energy methods to compute partition coefficients are generally more straight forward. For example, a 3D minimised structure of the solute can be generated with a simple tool such as babel and solvated to prepare the input  to compute a free energy of hydration. However, in these cases a careful choice of forcefield, as well as water models or organic solvents is essential. See for example~\cite{bosisio2016blinded,rustenburg2016measuring} for a good discussion on these choices. 
\todo[inline, color=green!20]{Just a note as a reminder: Chirality!}
%
%
%
%%%%%%%%%%%%
% Step 1   %
%%%%%%%%%%%%
%
\section{What simulation protocol should I choose? -- Step 2}
\label{sec:step2}
Alchemical free energy calculations can be grouped into two main categories, ``absolute'' and ``relative'' \footnote{The distinction is a bit of a misnomer, since both compute ratios of partition functions relative to another state, and neither computes an absolute free energy.}, which differ in whether they compute properties for a single molecule (absolute) or compare properties of different, usually closely related, molecules (relative).
To use binding as a concrete example, in absolute binding free energy calculations, one computes the binding free energy of a ligand to an individual receptor relative to a standard reference concentration.
In contrast, in relative binding free energy calculations, one compares the binding free energy of two related inhibitors to determine the potency difference.
\subsection*{Absolute and relative free energy calculations have some differences}
Many of the issues of setup and protocol for alchemical calculations are common, but some are different between absolute and relative calculations, so before treating the common elements we consider the protocol differences.

@@

Hybrid topology calculations have seen much less use but essentially consist of two absolute free energy calculations in opposite directions at the same time (turning one molecule off while turning the other on)~\cite{jiang2019computing}.
At present, the most widely used approaches, such as in Schrodinger's FEP+~\cite{wang2019protein} and in FESetup~\cite{loeffler2015fesetup} (for which calculations may be planned with Lead Optimization Mapper (LOMAP)~\cite{liu2013lead} seem to use single topology approaches, though some codes only support dual topology.
To our knowledge efficiency differences have not been thoroughly explored, though conventional wisdom suggests that fewer dummy atoms are better~\cite{liu2013lead,mobley2012perspective}.

@@

\paragraph{Ring breaking and forming.} Relative free energy calculations for ring breaking and forming are particularly challenging/problematic, in part because relative calculations rely on the free energy contributions of dummy atoms canceling between different legs of the thermodynamic cycle~\cite{}, which may not be true whenever dummy atoms are involved in rings.
Some approaches have attempted to address this [ref Schrodinger] but a general solution is not yet in mainstream use.

@@

Charge corrections have also been explored, and are potentially a viable solution to this problem~\cite{} where artifacts introduced by finite-size effects are corrected numerically.
~\cite{}). (chen et al J. Chem. Theory Comput. 2018, 14, 12, 6346-6358) However, application of such corrections typically remains less common than the use of a co-alchemical ion.

@@

As mentioned above, relative calculations introduce additional choices, including whether to define explicit intermediate states~\cite{} or leave these implicitly defined by the code~\cite{}.
Typically in single topology relative calculations it proves most efficient to first remove electrostatic interactions of any atoms which will be deleted, then modify other nonbonded interactions, then restore electrostatic interactions of any atoms which are being inserted.
Other schemes, such as simultaneously changing electrostatic and Lennard-Jones interactions, even with electrostatic ``soft core'' potentials, in our experience typically introduce errors and/or instabilities or are at least unreliable.
It is expected that similar considerations will apply to dual topology calculations, and the principle of first removing electrostatics and then removing steric interactions will likely serve well.

@@

%%%%%%%%%%%%%%%%%%%%
%              Terminology                  %
%%%%%%%%%%%%%%%%%%%%
\section{Terminology and abbreviations}
\label{sec:tem-abbrev}
\begin{itemize}
\item Feature Box covering major technical terms and abbreviations
\item Examples:
\begin{itemize}
\item EXP, BAR, MBAR
\item Double decoupling, single-topology, dual-topology, hybrid-topology, coupled-topology
\item FEP (free energy peturbation), alchemical, AFE (alchemical free energy)
\end{itemize}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%
%                Software                    %
%%%%%%%%%%%%%%%%%%%%
\section{Available software -- a summary}
\todo[inline]{Samar: write section}
\label{sec:software}
There are several softwares availble for carrying out alchemical free energy calculations. In this section we discuss some of the popular commercial and free tools along with their features. 
\begin{itemize}
\item Commercial:
   \begin{itemize}
    \item FEP+ is a tool offered by Schrodinger Inc. under a commercial license. It has an intuitive GUI which makes it easier for non-experts to run alchemical free energy calculations and analyze the results. It runs DESMOND MD package under the hood and hence parallelizes very well on the GPUs. 
    \end{itemize}
\item Free or low-cost for academics / commercial for industry:
	\begin{itemize}
	\item CHARMM has a variety of tools developed over the years. PERT module can be used to define initial and final states and define the intermediate lambda points. FREN and BAR modules can be used to analyze the data after the MD run. Lambda-dynamics based free energy calulation can be carried out using the BLOCK module.  
	\item TIES and AMBER FEW? (Peter Coveney)
	\item AMBER, including its new pmemd.cuda version support free energy calculation. 
	\end{itemize}
\item Free (libre) open source:
	\begin{itemize}
	\item PLUMED is an open source tool which enables the usage of a variety of MD engines. It is designed as a plugin for MD packages such that it analyzes the trajectory on the fly. It also offers a VMD based plugin for the computation of collective variables.   	
	\item SIRE  is a free, open source, multiscale molecular simulation framework, written to allow computational modellers to quickly prototype and develop new algorithms for molecular simulation and molecular design. 
	\item YANK is a tool developed by John Chodera and group on the top of OpenMM MD package. It allows the users to write their inputs in easy-to-use YAML format.
	\item GROMACS is a molecular simulation package with a significant number of free energy methods implementations. The LiveCOMS GROMACS tutorial has an example free energy calculation~\cite{lemkul2018From}.
	\item pmx for mutations
	\end{itemize}
\item Setup tools
	\begin{itemize}
	\item FESetup: AMBER, gromacs, Sire
	\item Lomap/Lomap2 : Relative alchemical transformation graph planning
	\item CHARMM-GUI is a web based tool for setting up a variety of MD simulations. It can be used to generate CHARMM scripts for solvation and ligand-binding free energy calculations.
	\end{itemize}
\item Analysis tools:
	\begin{itemize}
	\item Free Energy Workflows: Sire-specific free energy map analysis using weighted path averages
	\url{https://github.com/michellab/freenrgworkflows}
	\item Alchemlyb: Multipackage free energy analysis
	\url{https://github.com/alchemistry/alchemlyb}
	\item pymbar: MBAR implementation, but have to roll your own analysis wrapper
	\url{https://github.com/choderalab/pymbar}
	\end{itemize}
\end{itemize}

>>>>

Furthermore, are available computational resources sufficient that throughput will be

@@

Running binding FE calculations in a drug discovery application will typically require the use of software or tools to facilitate the calculations of many compounds. The commercial implementation from Schr\"{o}dinger, FEP+, uses a graphical user interface and once the user has calculated any missing force field parameters, calculations can be prepared and submitted within minutes. The software builds the network of perturbations, connecting similar compounds based on LOMAP methodology~\cite{liu2013lead}, all inputs for the Desmond simulations are built automatically and the job can be saved or run immediately on available GPUs. The cost of this software is often prohibitive but alternative tools are becoming available to allow relatively straight forward running of alchemical FE calculations with other software~\cite{gapsys2015pmx, loeffler2015fesetup} (CITE New Merz paper, cite PMX paper Vytas and Bert de Groot, cite FESETUP, cite FEanalysis). One consideration at this point is to define the perturbations suitable for the application. For instance, if the goal is to accurately assess the relative binding energy of a small number of compounds, possibly with challenging synthesis, the map of perturbations may contain as many connections between compounds as affordable. However, when running calculations on hundreds of compounds a so called ‘star-map’ can be used that just contains one connection per compound: perturbing every compound to a central ligand, typically the crystal structure ligand. In this way the top-ranking examples can be readily identified and submitted to additional calculations in a second round. 

@@

For binding free energy calculations using a congeneric set of ligands and therefore likely to be most suited to a relative free energy protocol (see~\ref{sec:step2}). Other than the choice of forcefield for the parameterization of the ligands, some care has to be taken selecting binding poses for these ligands. Generally a common assumption for a congeneric series is that the binding mode is conserved. Therefore, if an X-ray structure of one of the ligands is available, this should be used to position the ligands in the putative binding site in an energetically reasonable conformation that entails no steric or electrostatic mismatch with the receptor. Checking the X-ray structure versus the experimental electron densities is important, as the resolution of part of the ligand or important sidechains may be based on the interpretation of the crystallographer rather than the available electron density. For example, looking at a cyclohexane ring density, a chair conformation is vastly more likely than that of a boat and may just be poorly assigned.

Generally, binding modes within congeneric series are conserved~\cite{}, however, exceptions exist~\cite{}, and weaker binding compounds are more likely to adopt different binding modes (REFS). There may also be ambiguity about the relative orientation of substituents. A known issue involves a 180 degree flip in the dihedral angle of a 6-membered aromatic ring leading to a different spatial position of ortho- or meta- substituents that otherwise should overlap within a series. The 180 degree flip of the ring may not occur enough during simulations to overcome the starting configuration bias. Another scenario may be equatorial and axial substituted saturated rings (e.g. cyclohexane derivatives). This situation may be addressed by explicitly modelling different binding modes of the same ligand and combining later computed free energy differences for different binding modes into a relative free energies of binding~\cite{kaus2015how}.

Congeneric series can contain stereoisomers or enantiomers, making sure that you model the correct one is important. For racemates, the relative abundance of each stereoisomer is normally not known. Therefore, the experimental activity associated with just one conformation is more uncertain. However, the modeling typically uses just the bioactive conformation that best fits the active site. Clearly this introduces the chance for higher error versus experiment. Nevertheless, if all compounds in the congeneric series are racemic, originating from similar synthetic procedures with an expected similar abundance of stereoisomers, then the differences may cancel and the trend in calculated and observed binding energies may be robust. Nevertheless, we can see that care and further testing is needed in this scenario, and the quality of the predictions may suffer.

@@

Input coordinates for a congeneric series may be generated by docking calculations, or by ligand alignment using maximum common substructure algorithms. The latter tends to produce alignments that are more conserved and more consistent free energy changes across a dataset, but will struggle to yield reasonable results for relative binding free energy calculations that involve a significant binding mode rearrangement. This may also lead to steric clashes with the receptor coordinates of the reference ligand if structural rearrangements are needed to accommodate different members of the congeneric series. Small steric clashes may be resolved during subsequent simulation equilibration prior to data collection but there is a risk that the complex relaxes to an alternative metastable state. 
\todo[inline, color=green!20]{Just a note as a reminder: Chirality!}
An additional consideration arises for single topology relative free energy calculations. In this class of alchemical free energy calculations it is necessary to generate a molecular topology that may describe the initial and final states of the perturbation (see 7.1.1). In cases where the end-states have high topological similarity and high structural overlap this is relatively straightforward and typically handled by use of maximum common substructure calculations. In situations where the end-state topologies differ significantly, or there is relatively little spatial overlap between the two end-states some user intervention may be necessary to produce a satisfactory input topology.

If the binding site location is uncertain but the structure of the receptor is well defined and plausible binding sites are identified, it may be more useful to chose an absolute free energy protocol to compute the standard free energy of binding of the ligand to a set of binding sites. This requires the user to prepare input files describing the bound conformation in different putative binding sites (REF). The apparent binding free energy of the ligand may be obtained by combining the individual binding site free energies, which also indicate where the ligand is more likely to bind. In this case a docking program can generate initial structures. Different commercial and none commercial tools are available, such as: rDock, Autodock Vina, Glide, or Flare to name a few~\cite{ruiz-carmona2014rdock, trott2010autodock, friesner2004glide, cheeseright2006molecular}. 
If the putative binding sites are not apparent, for instance due to significant induced-fit effects, it may be challenging to obtain meaningful free energies of binding. One may have to account for the free energy change for forming a binding site in the target receptor which may not be feasible in FE simulation timescales. Another key application for absolute binding free energies is to study chemically different ligands, that do not share a common scaffold, but bind at the same site or the same site of similar proteins~\cite{aldeghi2015accurate}.

\subsection*{Free energies of hydration or partition coefficients}
Preliminary considerations necessary for using free energy methods to compute partition coefficients are generally more straight forward. For example, a 3D minimised structure of the solute can be generated with a simple tool such as babel and solvated to prepare the input  to compute a free energy of hydration. However, in these cases a careful choice of forcefield, as well as water models or organic solvents is essential. See for example~\cite{bosisio2016blinded,rustenburg2016measuring} for a good discussion on these choices.

%
%
%
%%%%%%%%%%%%
% Step 1   %
%%%%%%%%%%%%
%
\section{What simulation protocol should I choose? -- Step 2}
\label{sec:step2}
Alchemical free energy calculations can be grouped into two main categories, ``absolute'' and ``relative'' \footnote{The distinction is a bit of a misnomer, since both compute ratios of partition functions relative to another state, and neither computes an absolute free energy.}, which differ in whether they compute properties for a single molecule (absolute) or compare properties of different, usually closely related, molecules (relative).
To use binding as a concrete example, in absolute binding free energy calculations, one computes the binding free energy of a ligand to an individual receptor relative to a standard reference concentration.
In contrast, in relative binding free energy calculations, one compares the binding free energy of two related inhibitors to determine the potency difference.
\subsection*{Absolute and relative free energy calculations have some differences}
Many of the issues of setup and protocol for alchemical calculations are common, but some are different between absolute and relative calculations, so before treating the common elements we consider the protocol differences.

@@

Hybrid topology calculations have seen much less use but essentially consist of two absolute free energy calculations in opposite directions at the same time (turning one molecule off while turning the other on)~\cite{jiang2019computing}.
At present, the most widely used approaches, such as in Schr\"{o}dinger's FEP+~\cite{wang2019protein} and in FESetup~\cite{loeffler2015fesetup} (for which calculations may be planned with Lead Optimization Mapper (LOMAP)~\cite{liu2013lead} seem to use single topology approaches, though some codes only support dual topology.
To our knowledge efficiency differences have not been thoroughly explored, though conventional wisdom suggests that fewer dummy atoms are better~\cite{liu2013lead,mobley2012perspective}.

@@

\paragraph{Ring breaking and forming.} Relative free energy calculations for ring breaking and forming are particularly challenging/problematic, in part because relative calculations rely on the free energy contributions of dummy atoms canceling between different legs of the thermodynamic cycle~\cite{}, which may not be true whenever dummy atoms are involved in rings.
Some approaches have attempted to address this~\cite{clark2019relative} but a general solution is not yet in mainstream use.

@@

Charge corrections have also been explored, and are potentially a viable solution to this problem~\cite{} where artifacts introduced by finite-size effects are corrected numerically.
~\cite{chen2018accurate}). However, application of such corrections typically remains less common than the use of a co-alchemical ion.

@@

Relative calculations introduce additional choices, including whether to define explicit intermediate states~\cite{} or leave these implicitly defined by the code~\cite{}.
Typically in single topology relative calculations it proves most efficient to first remove electrostatic interactions of any atoms which will be deleted, then modify other nonbonded interactions, then restore electrostatic interactions of any atoms which are being inserted.
Other schemes, such as simultaneously changing electrostatic and Lennard-Jones interactions, even with electrostatic ``soft core'' potentials, in our experience typically introduce errors and/or instabilities or are at least unreliable.
It is expected that similar considerations will apply to dual topology calculations, and the principle of first removing electrostatics and then removing steric interactions will likely serve well.

@@

%%%%%%%%%%%%%%%%%%%%
%              Terminology                  %
%%%%%%%%%%%%%%%%%%%%
\section{Terminology and abbreviations}
\label{sec:tem-abbrev}
\begin{itemize}
\item Feature Box covering major technical terms and abbreviations
\item Examples:
\begin{itemize}
\item EXP, BAR, MBAR
\item Double decoupling, single-topology, dual-topology, hybrid-topology, coupled-topology
\item FEP (free energy peturbation), alchemical, AFE (alchemical free energy)
\end{itemize}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%
%                Software                    %
%%%%%%%%%%%%%%%%%%%%
\section{Available software -- a summary}
\todo[inline]{Samar: write section}
\label{sec:software}
There are several softwares availble for carrying out alchemical free energy calculations. In this section we discuss some of the popular commercial and free tools along with their features. 
\begin{itemize}
\item Commercial:
   \begin{itemize}
    \item FEP+ is a tool offered by Schr\"{o}dinger Inc. under a commercial license. It has an intuitive GUI which makes it easier for non-experts to run alchemical free energy calculations and analyze the results. It runs DESMOND MD package under the hood and hence parallelizes very well on the GPUs. 
    \end{itemize}
\item Free or low-cost for academics / commercial for industry:
	\begin{itemize}
	\item CHARMM has a variety of tools developed over the years. PERT module can be used to define initial and final states and define the intermediate lambda points. FREN and BAR modules can be used to analyze the data after the MD run. Lambda-dynamics based free energy calulation can be carried out using the BLOCK module.  
	\item TIES and AMBER FEW? (Peter Coveney)
	\item AMBER, including its new pmemd.cuda version support free energy calculation. 
	\end{itemize}
\item Free (libre) open source:
	\begin{itemize}
	\item PLUMED is an open source tool which enables the usage of a variety of MD engines. It is designed as a plugin for MD packages such that it analyzes the trajectory on the fly. It also offers a VMD based plugin for the computation of collective variables.   	
	\item SIRE  is a free, open source, multiscale molecular simulation framework, written to allow computational modellers to quickly prototype and develop new algorithms for molecular simulation and molecular design. 
	\item YANK is a tool developed by John Chodera and group on the top of OpenMM MD package. It allows the users to write their inputs in easy-to-use YAML format.
	\item GROMACS is a molecular simulation package with a significant number of free energy methods implementations. The LiveCOMS GROMACS tutorial has an example free energy calculation~\cite{lemkul2018From}.
	\item pmx for mutations
	\end{itemize}
\item Setup tools
	\begin{itemize}
	\item FESetup: AMBER, gromacs, Sire
	\item Lomap/Lomap2 : Relative alchemical transformation graph planning
	\item CHARMM-GUI is a web based tool for setting up a variety of MD simulations. It can be used to generate CHARMM scripts for solvation and ligand-binding free energy calculations.
	\end{itemize}
\item Analysis tools:
	\begin{itemize}
	\item Free Energy Workflows: Sire-specific free energy map analysis using weighted path averages
	\url{https://github.com/michellab/freenrgworkflows}
	\item Alchemlyb: Multipackage free energy analysis
	\url{https://github.com/alchemistry/alchemlyb}
	\item pymbar: MBAR implementation, but have to roll your own analysis wrapper
	\url{https://github.com/choderalab/pymbar}
	\end{itemize}
\end{itemize}
